Interval Probability for Fuzzy Quantum Theories

### 2016-06-09 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} Updating...

\yutsung{In \cite{Vourdas2014,Vourdas2015}, Vourdas made a comparison
between the additivity property of Kolmogorov probabilities 
\[
\delta\left(E_{1},E_{2}\right)=\pmeas\left(E_{1}\vee E_{2}\right)-\pmeas\left(E_{1}\right)-\pmeas\left(E_{2}\right)+\pmeas\left(E_{1}\wedge E_{2}\right)=0
\]
and its quantum counterpart 
\[
\mathfrak{D}\left(S_{1},S_{2}\right)=\Pi\left(S_{1}\vee S_{2}\right)-\Pi\left(S_{1}\right)-\Pi\left(S_{2}\right)+\Pi\left(S_{1}\wedge S_{2}\right)\textrm{ ,}
\]
where $S_{1}$ and $S_{2}$ are arbitrary linear spaces, and $\Pi$
maps a linear space to its projection operator. In the Dempster-Shafer
theory, the additivity property is relaxed such that $\delta\left(E_{1},E_{2}\right)\ge0$
for the lower probability or belief and $\delta\left(E_{1},E_{2}\right)\le0$
for the upper probability or plausibility. The sign of $\delta\left(E_{1},E_{2}\right)$
is then analog to $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
given the density matrix~$\rho$ since the non-additivity operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$
is non-zero when $S_{1}$ and $S_{2}$ does not commute.

@@

\begin{example}{[}Two-qubit quantum probability space{]} Consider
a two-qubit Hilbert space with the following subspaces:
\begin{eqnarray*}
S_{00} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{0}\right\} \right)\\
S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{+}\right\} \right)\\
S_{00}\wedge S_{0+} & = & \mathcal{O}=\left\{ 0\right\} \\
S_{00}\vee S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\right\} \right)\otimes\C^{2}
\end{eqnarray*}
 Then, their projection and non-additivity operators are 
\begin{eqnarray*}
\Pi\left(S_{00}\right) & = & \proj{0}\otimes\proj{0}\\
\Pi\left(S_{0+}\right) & = & \proj{0}\otimes\proj{+}\\
\Pi\left(S_{00}\wedge S_{0+}\right) & = & \mathbb{0}\otimes\mathbb{0}\\
\Pi\left(S_{00}\vee S_{0+}\right) & = & \proj{0}\otimes\mathbb{1}\\
\mathfrak{D}\left(S_{1},S_{2}\right) & = & \proj{0}\otimes\left(-\sigma_{x}-\sigma_{z}\right)
\end{eqnarray*}
We also consider the density matrix $\rho=a\proj{0}\otimes\proj{0}+\left(1-a\right)\proj{0}\otimes\proj{1}$
for $a\in\left[0,1\right]$. According to the Born rule, their probabilities
are
\begin{eqnarray*}
\Tr\left(\rho\Pi\left(S_{00}\right)\right) & = & a\\
\Tr\left(\rho\Pi\left(S_{0+}\right)\right) & = & \frac{1}{2}\left[a+\left(1-a\right)\right]=\frac{1}{2}\\
\Tr\left(\rho\Pi\left(S_{00}\wedge S_{0+}\right)\right) & = & 0\\
\Tr\left(\rho\Pi\left(S_{00}\vee S_{0+}\right)\right) & = & a+\left(1-a\right)=1
\end{eqnarray*}
and the non-additivity quantity~$\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\frac{1}{2}\left[-a+\left(1-a\right)\right]=\frac{1}{2}-a$.
However, I still don't have much intuition on why the probabilities
should have what kind of relations?\qed\end{example}

>>>>

\yutsung{In \cite{Vourdas2014,Vourdas2015}, Vourdas made a comparison
between the additivity property of Kolmogorov probabilities 
\[
\delta\left(E_{1},E_{2}\right)=\pmeas\left(E_{1}\vee E_{2}\right)-\pmeas\left(E_{1}\right)-\pmeas\left(E_{2}\right)+\pmeas\left(E_{1}\wedge E_{2}\right)=0
\]
and its quantum counterpart 
\[
\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\Tr\left(\rho\Pi\left(S_{1}\vee S_{2}\right)\right)-\Tr\left(\rho\Pi\left(S_{1}\right)\right)-\Tr\left(\rho\Pi\left(S_{2}\right)\right)+\Tr\left(\rho\Pi\left(S_{1}\wedge S_{2}\right)\right)\textrm{ ,}
\]
where $S_{1}$ and $S_{2}$ are arbitrary linear spaces, and $\Pi$
maps a linear space to its projection operator. While $\delta\left(E_{1},E_{2}\right)$
is always zero for Kolmogorov probabilities, the additivity property
of the Dempster-Shafer theory is relaxed to $\delta\left(E_{1},E_{2}\right)\ge0$
for the lower probability or belief and $\delta\left(E_{1},E_{2}\right)\le0$
for the upper probability or plausibility. The sign of $\delta\left(E_{1},E_{2}\right)$
is then analog to the sign of $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
given the density matrix~$\rho$ since the non-additivity operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$
is non-zero when $S_{1}$ and $S_{2}$ does not commute so that $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
is not always zero.

The Kolmogorov's $\delta\left(E_{1},E_{2}\right)=0$ is intuitive
because the relative frequencies of disjoint events should be additive
if the measurement is accurate. In the Dempster-Shafer theory, the
additivity property is modified because the imprecision of whether
an event happens or not is taken into account, but we can still decide
whether an instance belongs to different events concurrently. Applying
this idea to quantum, if we runs $N$ independent Stern-Galech

@@

\begin{example}[Two-qubit quantum probability space] Consider
a two-qubit Hilbert space with the following subspaces:
\begin{eqnarray*}
S_{00} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{0}\right\} \right)\\
S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\otimes\ket{+}\right\} \right)\\
S_{00}\wedge S_{0+} & = & \mathcal{O}=\left\{ 0\right\} \\
S_{00}\vee S_{0+} & = & \mathrm{span}\left(\left\{ \ket{0}\right\} \right)\otimes\C^{2}
\end{eqnarray*}
 Then, their projection and non-additivity operators are 
\begin{eqnarray*}
\Pi\left(S_{00}\right) & = & \proj{0}\otimes\proj{0}\\
\Pi\left(S_{0+}\right) & = & \proj{0}\otimes\proj{+}\\
\Pi\left(S_{00}\wedge S_{0+}\right) & = & \mathbb{0}\otimes\mathbb{0}\\
\Pi\left(S_{00}\vee S_{0+}\right) & = & \proj{0}\otimes\mathbb{1}\\
\mathfrak{D}\left(S_{1},S_{2}\right) & = & \proj{0}\otimes\left(-\sigma_{x}-\sigma_{z}\right)
\end{eqnarray*}
We also consider the density matrix $\rho=a\proj{0}\otimes\proj{0}+\left(1-a\right)\proj{0}\otimes\proj{1}$
for $a\in\left[0,1\right]$. According to the Born rule, their probabilities
are
\begin{eqnarray*}
\Tr\left(\rho\Pi\left(S_{00}\right)\right) & = & a\\
\Tr\left(\rho\Pi\left(S_{0+}\right)\right) & = & \frac{1}{2}\left[a+\left(1-a\right)\right]=\frac{1}{2}\\
\Tr\left(\rho\Pi\left(S_{00}\wedge S_{0+}\right)\right) & = & 0\\
\Tr\left(\rho\Pi\left(S_{00}\vee S_{0+}\right)\right) & = & a+\left(1-a\right)=1
\end{eqnarray*}
and the non-additivity quantity~$\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\frac{1}{2}\left[-a+\left(1-a\right)\right]=\frac{1}{2}-a$.
However, I still don't have much intuition on why the probabilities
should have what kind of relations?\qed\end{example}
